A Standard for the Scholarly Citation of Archaeological Data

### 2017-10-02 analysis/paper/paper.Rmd
investigate crevents as a source of citations

output: 
  papaja::apa6_word

@@

>>>>

output: 
  papaja::apa6_pdf:
   latex_engine: xelatex

@@

```{r events, eval = FALSE}
# get cross-ref events for dataset dois
# this is mostly citations of the datasets
library(crevents)

# contact the API and get the data...
cred_query_safe <- safely(cred_query)
events <- 
map(dc_arch$doi, ~cred_query_safe(rows = 10, 
                                  filter = list(`obj-id` = .x)))

saveRDS(events, "../data/raw_data/cross_ref_events.rds")

# Extract dataframes for analysis
events_df <- 
map_df(events, ~.x$result$message$events)
